---
title: "YuanChen_DC8"
author: "YuanChen"
date: '2022-10-18'
output: html_document
---

### STAT 184 Homework Exercises
```{r}
library(tidyverse)
library(dcData)
library(ggplot2)
library(mosaic)
```
##  Data Computing Chapter 8

Yuan Chen

##  Assign Exercises 

8.1, 8.2, 8.3

### Chapter 8 Exercises

##  Problem 8.1
Here are several functions from the ggplot2 graphics package used in DataComputing (in the text)

Match each of the functions to the task it performs.

### Construct the graphics frame
ggplot()

### Add a layer of glyphs
geom_point(), geom_histogram(), geom_segment()

### Set an axis label
ylab()

### Divide the frame into facets
facet_wrap() and facet_grid()

### Change the scale of the frame
scale_y_log10()

##  Problem 8.2
```{r}
frame <- CPS85 %>% 
  ggplot(aes(x = age, y = wage)) 
frame + geom_point(aes(color = married)) + facet_wrap(~sector) + coord_cartesian(xlim = c(20, 65), ylim = c(0,30))
```


##  Problem 8.3
```{r}
frame <- CPS85 %>%
  ggplot(aes(x = age, y = wage))
frame + geom_point(aes(color = married)) + facet_grid(sex~married) + coord_cartesian(xlim = c(15, 65), ylim = c(0, 45))
```





