---
title: "DC7"
author: "Yuan Chen"
date: '2022-09-26'
output: html_document
---
### STAT 184 Homework Exercises

##  Data Computing Chapter 7 

Yuan chen

##  Assign Exercises

7.3, 7.5, 7.6(Question 1 only), 7.7, 7.8

### Chapter 7 Exercises

##  Problem 7.3

```{r}
library(dcData)
library(tidyverse)
library(mosaic)
library(esquisse)
data("Minneapolis2013", package = "dcData")
```
1.There are 80101 cases
2.undervote, Mark Andrew, Bob Fine, Don Samules, undervotes
4. Bob Fine, Mark Andrew, Betsy Hodges
5.Besty Hodeges


### Problem 7.5

1. It group by the table by first and second 
2. It return the total number of case in the data
3. It count the total number of first and second
4. becasue we shuold group by first and then summarize.

### Problem 7.6

```{r}

data('ZipGeography', package = "dcData")
TotalLandArea <-
  dcData::ZipGeography %>%
  group_by(State) %>%
  summarise(LandArea = n()) %>%
  arrange(desc(LandArea))

Totalpopulation <-
  dcData::ZipGeography %>%
  group_by(State) %>%
  summarise(Population = n()) %>%
  arrange(desc(Population))


plot(TotalLandArea, Totalpopulation, main = "TotalLandArea vs Totalpopulation",
     xlab = "TotalLandArea", ylab = "Totalpopulation", pch = 1 )
```

### Question 7.7

a. sex, count, meanAge

b. diagnosis, count, meanAge

c. sex, diagnosis, count, meanAge

d. age, diagnosis, count, meanAge

e. age, count, meanAge


### Question 7.8
```{r}
ZipGeography %>%
 filter(!(Timezone %in% " ") | is.na(Timezone)) %>%
 ggplot() +
  aes(x = State, y = ZIP) +
  geom_tile(size = 1.2) +
  theme_minimal()
```



