---
title: "DC10"
author: "Yuan Chen"
date: '2022-10-03'
output: html_document
---

### STAT 184 Homework Exercises

##  Data Computing Chapter 10

Yuan Chen

##  Assign Exercises

10.3-10.6

##  Problem 10.3
1. nrow() 
2. str()
3. 
```{r}
install.packages("codebook")
data('codebook')
View('codebook')
```
4.  library(package)
5.
```{r}
install.packages("presidential")
library(dcData)
library(tidyverse)
data("presidential")
presidential %>%
  mutate(duration = end - start) %>%
  group_by(party) %>%
  summarise(total = n(),
            in_power = sum(duration))
```

##  Problem 10.4
1. The total count number from smallest to largest
2. Keeps all the female 
3. Return all the male
4. Total count of the babies
5. Only keeps the name and count 

##  Problem 10.5
```{r}
Minneapolis2013 %>%
  group_by(First = 'Ole Savior')%>%
  head(3)
```
1. 14399
2.
ABDUL M RAHAMAN “THE ROCK”	undervote
ABDUL M RAHAMAN “THE ROCK”	ABDUL M RAHAMAN “THE ROCK”
ABDUL M RAHAMAN “THE ROCK”	BETSY HODGES
3.
Undervote, Mark Andrew, Bob Fine

##  Problem 10.6
1.The largest are color J at 1.162137 carats
2.Color E at 114.0752 tables/carat.













