---
title: "YuanChen_DC5 and 6"
author: "Yuan Chen"
date: '2022-12-09'
output: html_document
---

## Assigned Exercises

- DC Chapter 5 Exercises:   5.2/5.3
- DC Chapter 6 Exercises:   6.1/6.3/6.5/6.6/6.7/6.8/6.9

## Load Required Packages

```{r}
rm(list = ls())

library(mosaicData)
library(mosaic)
library(tidyverse)
library(dcData)
```

## Chapter 5 Exercises

### Problem 5.1
```{r}
data("CPS85")
ggplot(data = CPS85, aes(x = sex, y = wage)) + 
  geom_boxplot()  + 
  aes(colour = married) + 
  facet_wrap(~race, ncol = 4) + 
  theme(legend.position = "right") + 
  labs(title = "")
```

### Problem 5.2
```{r}
data("NCHS")
ggplot( data = NCHS, aes(x = bmi)) + 
  geom_density(adjust = 0.83) + 
  aes(colour = sex) + 
  facet_wrap(~pregnant, ncol = 4) + 
  labs(title = "") + 
  theme(legend.position = "right") 

```

### Probelm 5.3

```{r}
ggplot(data = CPS85, aes(x = exper, y = wage)) +
  geom_point() + 
  aes(colour = married) +
  facet_wrap( ~ sector, ncol = 4) +
  scale_x_log10() +
  scale_y_log10() +
  theme_bw()
```


## Chapter 6

### Problem 6.1
#### “1433B”, “1433E”, “1433G”, “1433Z”
#### Yes; all x-axes represent the different cell conditions and y-axes represent the amount of substance.
#### *, vertical bars, red line segments

### Problem 6.2
#### Guides: y-axis tick marks, x-axis tick marks, color, fill, and sections of the x-axis concentration value corresponds to the y-position, genes correspond to x-position, molecules correspond to color, flux correspond to fill, target corresponds to placement on x-axis

#### Graphical attributes: color, fill, location molecule corresponds to color, flux corresponds to fill, concentration, target, and gene correspond to location of the dot

#### gene (x-axis) and concentration (y-axis)

#### gene and target

### Problem 6.3
Glyph 1: vertical bar with labeled dot, corresponds to ‘protein’ and its low/center/high properties
Glyph 2: stars, correspond to ‘signif’
Horizontal: defined by protein
Vertical: defined by low/center/high
Yes
Guides: y-axis tick marks, glyph labels, blue label saying “polarity proteins”

### Problem 6.4
Rectangle defined by time of day and different transportation routes
Solid lines, dashed lines, and dotted lines
Shape/Style: Solid lines are time on public transport, dashed lines are time between transfers, dotted lines are (most likely) walking time
Position: Time and route
Time of day, total travel time, type of transportation

### Problem 6.5
b: State (vertical axis) and Polling Organization (horizontal axis).

### Problem 6.6
d: Glyph: Rectangle. Graphical attribute: color and text.

### Problem 6.7
d: NYT poll probability for the Democratic candidate

### Problem 6.8
a: Vertical scale: name of state. e: Color: color band

### Problem 6.9
```{r}
Small <-
  NCHS %>%
  sample_n(size = 5000)
gf_point(weight ~ bmi, data = Small, color = ~ smoker) %>% 
  gf_theme(legend.position = "right") %>% 
  gf_labs(title = "", caption = "")
```
### Problem 6.10
Inner layer: Classification tree structure Outer layer: Colored bands
Inner scale: Division of space corresponding to the grouping of organisms Outer scale: Color corresponding to the type of molecule

